\textbf{Computational Fuzzy Extractors}

### 2013-05-14 trunk/notation.tex
adding notation file for lookup consistency

\documentclass[11pt]{article}
\def\shownotes{1}

@@

\mathchardef\mhyphen="2D

\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
\DeclareMathOperator*{\expe}{\mathbb{E}}

@@

\newcommand{\lwe}{\class{LWE}}
\newcommand{\LWE}{\class{LWE}}
\newcommand{\distLWE}{\ensuremath{\class{dist\mbox{-}LWE}}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}[theorem]{Construction}

\newcounter{ctr}
\newcounter{savectr}
\newcounter{ectr}

\newenvironment{newitemize}{%
\begin{list}{\mbox{}\hspace{5pt}$\bullet$\hfill}{\labelwidth=15pt%
\labelsep=5pt \leftmargin=20pt \topsep=3pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{3pt} }}{\end{list}}

\newenvironment{newenum}{%
\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=17pt%
\labelsep=5pt \leftmargin=22pt \topsep=3pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt} }}{\end{list}}

\newenvironment{tiret}{%
\begin{list}{\hspace{2pt}\rule[0.5ex]{6pt}{1pt}\hfill}{\labelwidth=15pt%
\labelsep=3pt \leftmargin=22pt \topsep=3pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt}}}{\end{list}}

\newenvironment{blocklist}{\begin{list}{}{\labelwidth=0pt%
\labelsep=0pt \leftmargin=0pt \topsep=10pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{20pt}}}{\end{list}}

\newenvironment{blocklistindented}{\begin{list}{}{\labelwidth=0pt%
\labelsep=30pt \leftmargin=30pt\topsep=5pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{10pt}}}{\end{list}}

\newenvironment{onelist}{%
\begin{list}{{\rm (\arabic{ctr})}\hfill}{\usecounter{ctr} \labelwidth=18pt%
\labelsep=7pt \leftmargin=25pt \topsep=2pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt} }}{\end{list}}

\newenvironment{twolist}{%
\begin{list}{{\rm (\arabic{ctr}.\arabic{ectr})}%
\hfill}{\usecounter{ectr} \labelwidth=26pt%
\labelsep=7pt \leftmargin=33pt \topsep=2pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{2pt} }}{\end{list}}

\newenvironment{centerlist}{%
\begin{list}{\mbox{}}{\labelwidth=0pt%
\labelsep=0pt \leftmargin=0pt \topsep=10pt%
\setlength{\listparindent}{\saveparindent}%
\setlength{\parsep}{\saveparskip}%
\setlength{\itemsep}{10pt} }}{\end{list}}

\newenvironment{newcenter}[1]{\begin{centerlist}\centering%
\item #1}{\end{centerlist}}

\newenvironment{codecenter}[1]{\begin{small}\begin{centerlist}\centering%
\item #1}{\end{centerlist}\end{small}}

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\xnote}[1]{{\authnote{Xianrui}{#1}}}

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vW}{\vect{W}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

\title{\textbf{Computational Fuzzy Extractors}}
\author{Benjamin Fuller%\footnote{The work of Benjamin Fuller is sponsored by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.}
 \and Xianrui Meng \and Leonid Reyzin}
\begin{document}
\maketitle

\begin{abstract} 
%\lnote{This is an old abstract, no longer correct}
Fuzzy extractors derive cryptographically strong keys from noisy sources.  They are traditionally built by combining a secure sketch and a randomness extractor.  Secure sketches remove noise from the source while revealing little information about the source.  Randomness extractors convert high entropy sources to the uniform distribution.  %Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  The minimal entropy loss 
%One-message information reconciliation protocols called secure sketches remove noise
%from secrets without revealing too much about them.  They are a crucial ingredient in
%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.

Secure sketches necessarily reveal some information about the noisy secret.
% and thus the key derived by fuzzy extractors has lower entropy than the source.  
The minimal entropy loss is dictated by bounds on error-correcting codes.  
Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
%suffer from similar bounds imposed by coding theory.

We ask whether these bounds can be overcome by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors.  %The answer we provide an answer for both secure sketches and fuzzy extractors.  
The answer to this question is mixed, For secure sketches the answer is no, and for fuzzy extractors the answer is yes.
\begin{itemize}
\item \textbf{Secure Sketches:} We show that a secure sketch that retains a large amount of HILL pseudo entropy implies a secure sketch which retains a similar amount of information-theoretic entropy.  We also consider a weaker computational notion of security, the unpredictability of a source conditioned on output of the secure sketch.  We show that in order to correct $t$ errors, the unpredictability of a source must decrease with the volume of a ball of radius $t$.
\item \textbf{Fuzzy Extractors:}  We show these impossibility results can be overcome by analyzing fuzzy extractors directly.  Namely, we show how to build a \emph{lossless} computational fuzzy extractor for uniform sources and certain other sources of high entropy~(namely, symbol-fixing sources, where each dimension is either uniform or fixed), based on the hardness of the Learning with Errors~(LWE) problem.  This construction requires us to show that the decision version of LWE is secure when a small number of dimension has no error---a result that may be of independent interest.
\end{itemize}
%mixed, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:
%
%\begin{itemize}
%\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.  We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.  We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.
%
%
%\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.  This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
%\end{itemize}
\end{abstract}

\newcommand{\M}{\mathcal{M}}
\section{Introduction}\label{sec:introduction}

Authentication generally requires a secret drawn from some high-entropy source.  One of the primary building blocks for authentication is reliable key derivation.  Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  %Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.

Fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} achieve reliable key derivation from noisy sources~(see \cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy} for applications of fuzzy extractors).  The setting 
%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
consists of  two algorithms: Generate (used once) and Reproduce (used subsequently).  The Generate ($\gen$) algorithm takes an input $w$ and produces a key $r$ and a public value $p$.  This information allows
the Reproduce ($\rep$) algorithm to reproduce $r$ given $p$ and some value $w'$ that is close to $w$ (according to some predefined metric, such as Hamming distance). 
Crucially for security,  knowledge of $p$ should not reveal $r$; that is, $r$ should be uniformly distributed conditioned on $p$.  This feature is needed because $p$ is not secret: for example, in a single-user setting (where the user wants to reproduce the key $r$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  The resulting secret key may be too short to be useful if the entropy loss is too high.  Traditionally, fuzzy extractors are defined as information-theoretic objects.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.

\bnote{This language is pretty clunky. Revise.}
The main novel tool in constructing fuzzy extractors is the secure sketch.  The secure sketch produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The security requirement is that $w$ has high min-entropy conditioned on $s$.  The key $r$ is formed by applying a randomness extractor~\cite{nisan1993randomness} to $w$.
%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high. 
The minimum entropy loss for secure sketches has been quantified in past work.  Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}, 
%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
the entropy loss of a secure sketch that can reconcile $t$ errors
 %with high probability 
 is bounded by the redundancy of
the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  Constructions of fuzzy extractors that use a secure sketch inherit this bound.
%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

\paragraph {Our Contributions}
To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.  Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.

On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.  We show that some entropy loss is necessary for secure sketches.
The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.  We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.  
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$.  Using an extractor with a reconstruction procedure would yield a pseudorandom key, see~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}.  We show lower bounds on the unpredictability loss of sketches.  We prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.

Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.  To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.

%to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.  This string $\recout$ is  required to have high HILL entropy even conditioned on $s$. Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
Computational extractors~\cite{krawczyk2010cryptographic, dachman2012computational} have the same goal in the setting without errors.  One way to achieve a computational (fuzzy) extractor is by using a computational extractor instead in place of the information theoretic extractor.  In particular, one technique is ``extract-then-expand'', where the output of a randomness extractor is stretched using a pseudorandom generator.  This construction is only possible if the entropy losses due to a secure sketch and information-theoretic extraction leave enough truly random bits.  We ask if a better solution is possible by making the entire process ``computational.''\bnote{Should add something about the Dana's result implying PRGs}

By considering a computational secrecy requirement, we construct the first \emph{lossless} (computational) fuzzy extractors, where the derived key $r$ is as long as the entropy of the source $w$\footnote{As noted above, using a computational extractor, in place of a information-theoretic extractor, allows a lossless construction.  However, this approach requires the computational extractor to work on the remaining entropy after the secure sketch.  We compare the two approaches in \secref{sec:prg based comparison}}. % without conditioning on anything---i.e., before $\gen$ is run (see~\thref{thm:lossless secure conductor log})).  
Our construction of lossless fuzzy extractors~(\consref{cons:informal construction}) is based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult.  
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
Our lossless fuzzy extractor is built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work.  To apply the LWE assumption, we correct errors of a random linear code which limits our decoding algorithm to reconciling a logarithmic number of differences.

The recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} shows the hardness of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.  This allows us to directly use our source $w$ as the LWE error vector.  To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution. We are able to relax this limitation and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (each dimension is either uniform or fixed). This relaxation requires new results about the hardness of LWE when samples have a fixed~(and adversarially known) error vector, which may be of independent interest~(\thref{thm:blockLWE}).

%Authentication generally requires secrets.  Unfortunately, many useful  sources that contain sufficient entropy for a secret  are also noisy, and provide similar, but not identical secret values at each invocation (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.
%
%We will specifically focus on a one-round information reconciliation  mechanism called ``secure sketch,''  which, aside from its immediate application to authentication, is also
%a crucial ingredient in the construction of fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08} (as well as in other contexts, e.g.,~\cite{Boyen05secureremote,dodisWichs2009,chandran2010privacy}).
%It consists of  two algorithms: Sketch (used once) and Recover (used subsequently).  The Sketch ($\sketch$) algorithm takes an input $w$ and produces a sketch $s$.  This information allows
%the Recover ($\rec$) algorithm to recover $w$ given $s$ and some value $w'$ that is close (according to some predefined metric, such as Hamming distance) to $w$. 
%Crucially for security,  knowledge of $s$ should not reveal $w$; that is, $w$ should still have entropy  conditioned on $s$.  This feature is needed because $s$ is not secret: for example, in a single-user setting (where the user wants to recover the original reading $w$ from a subsequent reading $w'$), it would be stored in the clear; and in a key agreement application~\cite{Boyen05secureremote} (where two parties have $w$ and $w'$, respectively), it would be transmitted between the parties.
%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, the entropy loss of a secure sketch is the difference in the entropy of $w$ and the entropy of $w$ conditioned on $s$.  
%
%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. For example, in the application of secure sketches to fuzzy extractors (whose goal is to reliably produce a uniformly random secret key from a noisy input), the resulting secret key may be too short to be useful if the entropy loss is too high. However, because secure sketches are defined as information-theoretic objects, some entropy loss is inherent in any secure sketch construction, because $s$ contains enough information to recover $w$ from any value $w'$ that is close to it.  
%
%The minimum necessary  entropy loss has been quantified in past work.  Even if we don't require perfect correctness (i.e., allow $\rec$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), the entropy loss of a secure sketch that can reconcile $t$ errors with high probability is bounded by the redundancy of
%the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}
%%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).
%
%\paragraph {Our Contributions}
%To see if entropy loss can be improved, we explore secure sketches with the relaxed secrecy requirement that is computational rather than information-theoretic.  
%The natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.  
%
%On the negative side, we show defining sketches using HILL entropy is unlikely to be fruitful. We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.
%%Furthermore, we have (asymptotic)~constructions that meet these bounds.
%
%On the positive side, we show that a different relaxation of the definition can in fact lead to a \emph{lossless} construction. The idea is to give up on reconstructing $w$ and, instead, to focus on producing a consistent string $\recout$  each time $\rec(w', s)$ is called.  This string $\recout$ is  required to have high HILL entropy even conditioned on $s$. Because this object \emph{conducts} the entropy from $w$ to $\recout$ and tolerates noise in its input, following \cite{CRVW02,KanukurthiR09}, we call it a \emph{computational fuzzy conductor}.
%
%Given this relaxation, we are able to build \emph{lossless} computational fuzzy conductors, in which the HILL entropy of $\recout$ conditioned on $s$ is the same as the entropy of $w$ without conditioning on anything---i.e., before $\sketch$ is run (see Theorem~%s~%\ref{thm:lossless secure sketch} and
%~\ref{thm:lossless secure conductor log})).  We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult. 
%
%We show that this relaxation of the security requirement is  useful.  Specifically, we also define the notion of computational fuzzy extractors, in which the extracted key is required to be pseudorandom---i.e., to look random to any computationally bounded observer.
%We show that our relaxed notion of secure sketches is sufficient to construct computational  fuzzy extractors via a simple and efficient construction, utilizing reconstructive extractors~\cite{barak-computational}.  The resulting fuzzy extractor produces a key that is as long as the entropy of $w$, minus only the loss necessary in any extractor construction.
%\lnote{it would be good to find another application} 
%
%Both our lossless fuzzy conductor and the resulting fuzzy extractor are built via the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} already used in prior work.  To be able to apply the LWE assumption, we use a random linear code (unfortunately, our decoding algorithm can only reconcile a logarithmic number of differences).  We utilize the recent result of D\"{o}ttling and M\"{u}ller-Quade~\cite{dottling2012} that shows security of LWE when the error vector comes from the uniform distribution, with each coordinate ranging over a small interval.  The LWE error vector, in our case, is the input $w$ itself.  To utilize the result of~\cite{dottling2012}, we need to assume that the input comes from the uniform distribution. We are able to relax this limitation somewhat and allow $w$ to come from a symbol-fixing source~\cite{KZ07} (where each dimension is either uniform or fixed). This relaxation requires new results about the hardness of LWE when samples have a fixed error vector, which may be of independent interest~(\thref{thm:blockLWE}).
\section{Preliminaries}
\label{sec:preliminaries}
For a random variable $X = X_1||...|| X_n$ where each $X_i$ is over some alphabet $Z$, we denote by $X_{1,..., k} = X_1||...|| X_k$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$, 
%the {\em (worst-case) conditional min-entropy} of $X$ given $Y$ is  $\Hoo(X|Y) = -\log(\max_{x,y} \Pr[X=x|Y=y])$, and
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.  
%The {\em collision probability} of  $X$ is 
%$\col(X) = \sum_{x} \Pr[X=x]^2$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$. %We write $X \approx_{\epsilon} Y$ if $\Delta(X,Y) \leq \epsilon$, and when $\epsilon$ is negligible (in the appropriate parameter, as clear from the context) then we say $X$ and $Y$ are \emph{statistically close}.  
For a distinguisher $D$~(or a class of distinguishers $\mathcal{D}$) we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$.  We denote by $\mathcal{D}_{s_{sec}}$ the class of randomized circuits which output a single bit and have size at most $s_{sec}$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t(\cdot)|$ the size of a ball of radius $t$.  For the Hamming metric over $Z^n$ the size of $B_t(\cdot) = \sum_{i=0}^t {n \choose t} (|Z|-1)^i $, for clarity we express this value as $B_t(\cdot)$.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.
We use bold letters for vectors or matrices, capitalized letters to be random variables, and lower case letters for the elements in the vector or samples from a random variable.

\subsection{Fuzzy Extractors and Secure Sketches}
\label{sec:fuzzy extractors}

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.% \lnote{$d$ is overloaded -- it's also a seed length for an extractor and also a constant in the parameter setting.  can we change this $d$ to $\mathsf{dis}$?}

\begin{definition}%\protect{\cite[Definition 5]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties:
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $R\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

Secure sketches are the main technical tool in the construction of fuzzy extractors.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}%\protect{\cite[Definition 3]{DBLP:journals/siamcomp/DodisORS08}}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

Note that in the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}):

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^m$ a \emph{$(k, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge k$, we have $\Delta((\ext(X, U_d), U_d, Y), U_m\times
U_d \times Y) \le \epsilon$.
\end{definition}

>>>>

\documentclass[11pt]{article}

@@

@@

\begin{document}
Notation:
\begin{itemize}
\item $B_t(x)$ - the ball of radius $t$ around a point $x$
\item $\sketch$ - secure sketch procedure
\item $\rec$ - recover procedure for secure sketch
\item $\gen$ - fuzzy extractor generate
\item $\rep$ - fuzzy extractor reproduce
\item $w/W$ - the noisy source we are drawing from
\item $s$ - output of secure sketch
\item $S$ - the distribution W is conditioned on, we also denote this by $\sketch(W)$
\item $R$ - key from fuzzy extractor
\item $P$ - helper value for fuzzy extractor
\item $X, Y$ - these are used for the indistinguishable distributions, for the $\hill$ and $\unp$ entropy.
\item $D, \mathcal{D}$ - distinguisher and distinguisher class
\item $Z$ - the alphabet when we consider Hamming metric
\item $\ell$ - derived key length
\item $\epsilon$ - distance from uniform either for extractor or fuzzy extractor
\item $\delta$ - error rate of a fuzzy extractor or secure sketch
\item $\ext$ - extractor
\item $\rext$ - reconstructive extractor
\item $(\mathcal{M}, \dis)$ - metric space and associated distance
\item $s_{sam}$ - size of $\sample$
\item $s_{sec}$ - size of security circuit
\item $s_{rec}$ - size of recover circuit
\item $t$- bounded such that $\dis(w, w')\leq t$
\item $k$- the number of hardcore dimensions in AKV09, this is the size of our resulting key
\item $m$- starting min-entropy of source
\item $\tilde{m}$ - resulting min-entropy of a construction
\item $\vect{A}$ - random matrix in LWE
\item $n$ - security parameter for LWE
\item $q$ - size of field for LWE
\item $m$ - number of samples in LWE
\item $\vect{x} / X$ - secret vector in LWE
\item $\chi$ - arbitrary error distribution for LWE
\item $\bar{\Psi}_\alpha$ - discretized Gaussian distribution
\item $\gamma$ - Parameter in DMQ error size and lattice hardness
\item $d$ - running time of inverter, tied to number of errors that can be corrected and redundancy in m
\item $c$ - constant log errors that can be corrected
\item $\rho$ - $\rho q$ is the noise width
\item $b$ - the number of bits in a block $b = \log \rho q$
\item $\mathcal{C}$ - a set that forms a code
\item $C$ - a distribution of points that we use to form a code
\item $C, D$ - the reconstruction procedures for a reconstructive extractor
   NOTE: both of these are used above, need to change
\item $\neigh , s_{neigh}$- algorithm for sampling a neighbor
\item $\sample, s_{sam} $- algorithm for picking a random point in the metric space
\item $\vect{C}, \vect{D} $ used in the decoding algorithms of code-offset construction
\item $f$ - the degree of the polynomial used to express the size of the field q
\item $n_0$ - first point where LWE is considered secure
\item $\alpha$ - the number of fixed dimensions for a block fixing source
\item $\beta$ - the extra variables added in Theorem 5.3
\item $\gamma$ - parameter in DMQ13, slightly changes their setting, we consider $\gamma = 1/2$
\item $g$ - the fraction of n that we will output as hardcore bits
\end{itemize}

\end{document}
